Incorporating dive behaviour into models of marine animal movement

### 2018-10-03 manuscript/manuscript_template.Rmd
Update manuscript to include outline abstract

---
title:  'A template for writing a manuscript in Rmarkdown'
author:
- James Grecian One^[University of Somewhere]
- Ian Jonsen Two^[University of Nowhere]
date: "`r format(Sys.time(), '%d %B %Y')`"
tags: [nothing, nothingness]
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
csl: mee.csl
header-includes:
   - \usepackage{lineno}
   - \linenumbers
---

@@

# Abstract

*Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.*

# Introduction

@@

Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel, id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.

Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes percipitur at vis. Numquam similique in per, te quo saepe utroque pericula.

Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne suas latine vix, eos oblique sanctus pertinax cu.

# Methods

@@

Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel, id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.

@@

The relationship was first described by
`r citet("10.1111/j.1461-0248.2005.00827.x")`. However, there are also opinions
that the relationship is spurious `r citep("10.1111/j.2041-210x.2012.00264.x")`.
We used R for our calculations `r citep(citation())`, and we used package `knitcitations` `r citep(citation("knitcitations"))` to make the bibliography.

# Results and discussion

@@

Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel, id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.

Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes percipitur at vis. Numquam similique in per, te quo saepe utroque pericula.

Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne suas latine vix, eos oblique sanctus pertinax cu.

# References

```{r, warning=FALSE, message=FALSE, echo=FALSE} 
  write.bibtex(file="references.bib")
```

>>>>

---
title:  'Incorporating dive behaviour into models of marine animal movement'

author: |
  | W. J. Grecian$^1$ ^[Corresponding author: james.grecian@gmail.com] , I. D. Jonsen$^2$
  | $^1$Sea Mammal Research Unit, Scottish Oceans Institute, University of St Andrews
  | $^2$Dept. of Biological Sciences, Macquarie University, Sydney, Australia

abstract: |
 The Abstract must not exceed 350 words and should list the main results and conclusions, using simple, factual, numbered statements.  
 1. Models of animal movement often only consider horizontal movement over 2 dimensions. Incorporating vertical movement in these models offers the potential to improve our understanding of the drivers of animal movement.  
 2. Here we describe a state-space model that incorporates a random walk on both horizontal and vertical movements, and estimates the covariance between them. The model is flexible to allow both parameters to be conditioned on covariates, offering insights into the drivers of animal movement.  
 3. outline the main results  
 4. identify the conclusions and the wider implications.

keywords: | 
 A list in alphabetical order not exceeding eight words or short phrases. The most important key-words should appear in the title and the abstract as well as the key-word list.

date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
csl: mee.csl
#bibliography: references.bib
header-includes:
   - \usepackage{lineno}
   - \linenumbers
---

@@

# INTRODUCTION

@@

# MATERIALS AND METHODS

@@

@@

The relationship was first described by @Halpern_2006. However, there are also opinions
that the relationship is spurious [@Keil_2012].
We used R for our calculations [@R_Core_Team_2016], and we used package `knitcitations` [@Boettiger_2017] to make the bibliography.

# RESULTS

@@

# DISCUSSION

# CONCLUSION

# ACKNOWLEDGEMENTS

This project was made possible through a travel award from the Canada-UK Foundation.

# AUTHORS' CONTRIBUTION

# DATA ACCESSIBILITY

# REFERENCES

```{r, warning=FALSE, message=FALSE, echo=FALSE} 
  #write.bibtex(file="references.bib")
```

### 2018-10-03 manuscript/manuscript_template.tex
Update manuscript to include outline abstract

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={A template for writing a manuscript in Rmarkdown},
            pdfauthor={James Grecian One; Ian Jonsen Two},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{A template for writing a manuscript in Rmarkdown}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{James Grecian One\footnote{University of Somewhere} \\ Ian Jonsen Two\footnote{University of Nowhere}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{21 September 2018}

@@

\begin{document}
\maketitle

\section{Abstract}\label{abstract}

\emph{Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel
erat falli ut. Feugiat legendos adipisci vix at, usu at laoreet
argumentum suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor
liberavisse sea. Ponderum vivendum te nec, id agam brute disputando
mei.}

\section{Introduction}\label{introduction}

@@

Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando
debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis
singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,
id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id
usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum
conceptam.

Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit
quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos
ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes
percipitur at vis. Numquam similique in per, te quo saepe utroque
pericula.

Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo
vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque
gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne
suas latine vix, eos oblique sanctus pertinax cu.

\section{Methods}\label{methods}

@@

\begin{longtable}[]{@{}lrrrr@{}}
\caption{This is a GLM summary table.}\tabularnewline
\toprule
& Estimate & Std. Error & t value &
Pr(\textgreater{}\textbar{}t\textbar{})\tabularnewline
\midrule
\endfirsthead
\toprule
& Estimate & Std. Error & t value &
Pr(\textgreater{}\textbar{}t\textbar{})\tabularnewline
\midrule
\endhead
(Intercept) & 0.05 & 0.1 & 0.48 & 0.63\tabularnewline
x & 1.96 & 0.1 & 19.68 & 0.00\tabularnewline
\bottomrule
\end{longtable}

@@

The relationship was first described by @Halpern\_2006. However, there
are also opinions that the relationship is spurious {[}@Keil\_2012{]}.
We used R for our calculations {[}@R\_Core\_Team\_2017{]}, and we used
package \texttt{knitcitations} {[}@Boettiger\_2017{]} to make the
bibliography.

\section{Results and discussion}\label{results-and-discussion}

@@

Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando
debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis
singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,
id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id
usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum
conceptam.

Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit
quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos
ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes
percipitur at vis. Numquam similique in per, te quo saepe utroque
pericula.

Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo
vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque
gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne
suas latine vix, eos oblique sanctus pertinax cu.

\section{References}\label{references}

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Incorporating dive behaviour into models of marine animal movement},
            pdfkeywords={A list in alphabetical order not exceeding eight words or short phrases.
The most important key-words should appear in the title and the abstract
as well as the key-word list.},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Incorporating dive behaviour into models of marine animal movement}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{W. J. Grecian\(^1\) \footnote{Corresponding author:
  \href{mailto:james.grecian@gmail.com}{\nolinkurl{james.grecian@gmail.com}}}
, I. D. Jonsen\(^2\)\\
\(^1\)Sea Mammal Research Unit, Scottish Oceans Institute, University of
St Andrews\\
\(^2\)Dept. of Biological Sciences, Macquarie University, Sydney,
Australia}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{03 October 2018}

@@

\begin{document}
\maketitle
\begin{abstract}
The Abstract must not exceed 350 words and should list the main results
and conclusions, using simple, factual, numbered statements.\\
1. Models of animal movement often only consider horizontal movement
over 2 dimensions. Incorporating vertical movement in these models
offers the potential to improve our understanding of the drivers of
animal movement.\\
2. Here we describe a state-space model that incorporates a random walk
on both horizontal and vertical movements, and estimates the covariance
between them. The model is flexible to allow both parameters to be
conditioned on covariates, offering insights into the drivers of animal
movement.\\
3. outline the main results\\
4. identify the conclusions and the wider implications.
\end{abstract}

\section{INTRODUCTION}\label{introduction}

@@

\section{MATERIALS AND METHODS}\label{materials-and-methods}

@@

\begin{longtable}[]{@{}lrrrr@{}}
\caption{This is a GLM summary table.}\tabularnewline
\toprule
& Estimate & Std. Error & t value &
Pr(\textgreater{}\textbar{}t\textbar{})\tabularnewline
\midrule
\endfirsthead
\toprule
& Estimate & Std. Error & t value &
Pr(\textgreater{}\textbar{}t\textbar{})\tabularnewline
\midrule
\endhead
(Intercept) & 0.01 & 0.10 & 0.07 & 0.94\tabularnewline
x & 1.83 & 0.11 & 16.95 & 0.00\tabularnewline
\bottomrule
\end{longtable}

@@

The relationship was first described by @Halpern\_2006. However, there
are also opinions that the relationship is spurious {[}@Keil\_2012{]}.
We used R for our calculations {[}@R\_Core\_Team\_2016{]}, and we used
package \texttt{knitcitations} {[}@Boettiger\_2017{]} to make the
bibliography.

\section{RESULTS}\label{results}

@@

\section{DISCUSSION}\label{discussion}

\section{CONCLUSION}\label{conclusion}

\section{ACKNOWLEDGEMENTS}\label{acknowledgements}

This project was made possible through a travel award from the Canada-UK
Foundation.

\section{AUTHORS' CONTRIBUTION}\label{authors-contribution}

\section{DATA ACCESSIBILITY}\label{data-accessibility}

\section{REFERENCES}\label{references}
